Model Adaptivity for Goal-Oriented Inference using Adjoints

### 2016-12-15 paper/paper_v4_cmame.tex
added missing abstract

\author[adr1]{Harriet Li\corref{cor1}}
\cortext[cor1]{Corresponding author. \textit{Email address: kameeko@mit.edu}}
\address[adr1]{Department of Aeronautics and Astronautics, Massachusetts Institute of Technology, Cambridge, MA, 02139, USA; \texttt{kameeko@mit.edu}}
\author[adr2]{Vikram Garg}
\address[adr2]{Institute for Computational Engineering and Sciences, University of Texas, Austin, TX, 78712, USA; \texttt{vikram.v.garg@gmail.com}}
\author[adr3]{Karen Willcox}
\address[adr3]{Department of Aeronautics and Astronautics, Massachusetts Institute of Technology, Cambridge, MA, 02139, USA; \texttt{kwillcox@mit.edu}}

>>>>

\author[adr1]{Harriet Li\corref{cor1}}
\cortext[cor1]{Corresponding author. \textit{Email address: hli@alum.mit.edu}}
\address[adr1]{Department of Aeronautics and Astronautics, Massachusetts Institute of Technology, Cambridge, MA, 02139, USA; \texttt{hli@alum.mit.edu}}
\author[adr2]{Vikram Garg}
\address[adr2]{Institute for Computational Engineering and Sciences, University of Texas, Austin, TX, 78712, USA; \texttt{vikram.v.garg@gmail.com}}
\author[adr3]{Karen Willcox}
\address[adr3]{Department of Aeronautics and Astronautics, Massachusetts Institute of Technology, Cambridge, MA, 02139, USA; \texttt{kwillcox@mit.edu}}
